Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-07 supplement/math-env/math-example.tex
updates to examples sections

\subsubsection{Pandoc Handling, extensions}
As \CRANpkg{texor} calls \CRANpkg{rmarkdown} to render the Rmarkdwon file into HTML,
the \verb|rjtools::rjournal_web_article| template by default uses MathJax as the math engine. 
Also we specify the Mathjax version in the metadata of the generated Rmarkdown file.

>>>>

\subsubsection{Pandoc Handling, extensions}
As \CRANpkg{texor} calls \CRANpkg{rmarkdown} to render the Rmarkdown file into HTML,
the \verb|rjtools::rjournal_web_article| template by default uses MathJax as the math engine. 
Also we specify the Mathjax version in the metadata of the generated Rmarkdown file.

### 2023-08-07 texor.Rmd
updates to examples sections

The format is constantly evolving. Early articles were typeset using LateX [@latex], from a specific, but changing, template. This requires that code is separated from the documentation, and there is a chance that code chunks in the paper don't reproduce the results reported. With the emergence of dynamic document systems like R Markdown [@rmarkdown] a tight-coupling of code and documentation is possible. Code chunks are dynamically executed when the document is typeset using a system like \CRANpkg{knitr} [@knitr], making reporting of computing research more reproducible.

@@

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, additional pre-processing needs to be done to handle special R Journal LaTeX styling. And further post-processing needs to be done to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and postprocessing of the document.

@@

**DC: Add a diagram here showing flow of work, just pre-process .tex -> pandoc -> lua ; rebib operations???**

@@

This is handled by pre-rpocessing the LaTeX to create the image, as both PDF, and them PNG, for inclusion in the R Markdown document using:

@@

Interestingly, some legacy articles have algorithms are defined in the figure environment:

@@

@@

@@

Only handling to html format, especially relevant for figures, because the legacy pdf will remain the same. If using for converting work from LaTeX to Rmd then this will need manual changing by author. See rjtools guide.

>>>>

The format is regularly updated. Early articles were typeset using LateX [@latex], from a specific, but changing, template. This requires that code is separated from the documentation, and there is a chance that code chunks in the paper don't reproduce the results reported. With the emergence of dynamic document systems like R Markdown [@rmarkdown] a tight-coupling of code and documentation is possible. Code chunks are dynamically executed when the document is typeset using a system like \CRANpkg{knitr} [@knitr], making reporting of computing research more reproducible.

@@

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, additional pre-processing needs to be done to handle special R Journal LaTeX styling. And further post-processing needs to be done to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and post-processing of the document, in a workflow illustrated in Figure \@ref(fig:workflow).

@@

```{r workflow, fig.cap="Workflow of the document conversion conducted by texor."}
knitr::include_graphics("workflow.png")
```

@@

This is handled by pre-processing the LaTeX to create the image, as both PDF, and them PNG, for inclusion in the R Markdown document using:

@@

Algorithms as figures is supported, and the following description will yield the result in Algorithm \@ref(alg:how).

@@

<figure id="alg:how">
<img src="alghow.png" style="width:100.0%" />
<p>initialization</p>
<figcaption>Algorithm 1: How to write algorithms</figcaption>
</figure>

**DC: Don't really understand this example, why would html figure definition also create pdf?**

@@

Math is handled primarily by pandoc. The inline math and equation descriptions are unchanged between LaTeX and R Markdown.

The HTML output renders math using MathJax. This does mean that some functionality, like `\bm`, `\boldmath` and `mathbb` not supported, and special definitions cannot be handled.

The numbering of equations is a bit trickier. LaTeX automatically numbers equations, unless specifically instructed not to. Equation numbering in R Markdown requires specific labelling using `(\#eq:xx)` as described in @bookdown. The \CRANpkg{texor} helps by adding the labelling using a Lua filter to convert the existing `\label{..}` to `(\#eq:xx)`.

@@

Remember only the HTML is rendered, and the original PDF is not re-generated.

Only handling to HTML format, especially relevant for figures, because the legacy pdf will remain the same. If using for converting work from LaTeX to Rmd then this will need manual changing by author. See rjtools guide.

### 2023-08-07 texor.tex
updates to examples sections

The format is constantly evolving. Early articles were typeset using LateX (The LaTeX Project 2023), from a specific, but changing, template. This requires that code is separated from the documentation, and there is a chance that code chunks in the paper don't reproduce the results reported. With the emergence of dynamic document systems like R Markdown (Xie, Allaire, and Grolemund 2018) a tight-coupling of code and documentation is possible. Code chunks are dynamically executed when the document is typeset using a system like \CRANpkg{knitr} (Xie 2015), making reporting of computing research more reproducible.

@@

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, additional pre-processing needs to be done to handle special R Journal LaTeX styling. And further post-processing needs to be done to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and postprocessing of the document.

\textbf{DC: Add a diagram here showing flow of work, just pre-process .tex -\textgreater{} pandoc -\textgreater{} lua ; rebib operations???}

@@

Interestingly, some legacy articles have algorithms are defined in the figure environment:

@@

@@

@@

>>>>

The format is regularly updated. Early articles were typeset using LateX (The LaTeX Project 2023), from a specific, but changing, template. This requires that code is separated from the documentation, and there is a chance that code chunks in the paper don't reproduce the results reported. With the emergence of dynamic document systems like R Markdown (Xie, Allaire, and Grolemund 2018) a tight-coupling of code and documentation is possible. Code chunks are dynamically executed when the document is typeset using a system like \CRANpkg{knitr} (Xie 2015), making reporting of computing research more reproducible.

@@

Pandoc can be used to do the conversion from LaTeX to R Markdown also. However, additional pre-processing needs to be done to handle special R Journal LaTeX styling. And further post-processing needs to be done to handle specific R Journal R Markdown styling. The \CRANpkg{texor} package contains functionality to handle this pre- and post-processing of the document, in a workflow illustrated in Figure \ref{fig:workflow}.

\begin{figure}
\includegraphics[width=15.5in]{workflow} \caption{Workflow of the document conversion conducted by texor.}\label{fig:workflow}
\end{figure}

@@

Algorithms as figures is supported, and the following description will yield the result in Algorithm \ref{alg:how}.

@@

initialization

Algorithm 1: How to write algorithms

\textbf{DC: Don't really understand this example, why would html figure definition also create pdf?}

@@

Math is handled primarily by pandoc. The inline math and equation descriptions are unchanged between LaTeX and R Markdown.

The HTML output renders math using MathJax. This does mean that some functionality, like \texttt{\textbackslash{}bm}, \texttt{\textbackslash{}boldmath} and \texttt{mathbb} not supported, and special definitions cannot be handled.

The numbering of equations is a bit trickier. LaTeX automatically numbers equations, unless specifically instructed not to. Equation numbering in R Markdown requires specific labelling using \texttt{(\textbackslash{}\#eq:xx)} as described in Yihui Xie (2023). The \CRANpkg{texor} helps by adding the labelling using a Lua filter to convert the existing \texttt{\textbackslash{}label\{..\}} to \texttt{(\textbackslash{}\#eq:xx)}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-bookdown}{}}%
Yihui Xie. 2023. \emph{{bookdown: Authoring Books and Technical Documents with R Markdown}}. \#equations. \url{https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html}.
